Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-03-07 ms_pre_post.Rmd
Another comment -- maybe shorten later

>>>>

<!---If we're spending this much time justifying an assumption, then we should be able to explain *why* it's an important assumption *with respect to addressing our questions* (there are hundreds of other assumptions we don't spend time on -- number of loci probably isn't going to affect our take-home message). If we can't, and the answer is that 'we don't know if it's important or not', then we're probably not doing theory very well. Actually, I don't think the nature of the costs is going to be important because it's not going to affect any key hypotheses that might be derived from our model -- the effect of a direct negative cost has a very clear interpretatation; changing how a cost is paid might quantitatively affect the end *net* cost as a counter-balance to selection, but so will changing the exact values of the costs we do use. There's no good reason to believe that the way a cost is paid will affect any of the major conclusions (degeneracy is important, polyandry is more likely to evolve given post-copulatory selection, etc.) except by tweaking the overall net cost countering adaptive benefit of inbreeding avoidance (alternatively, if we *can* think of one, it would be a great opportunity for another theory paper!). --->
